### 2024-05-16 2-layer.tex
Adding minor corrections from viva/annotated thesis

\begin{center}
\begin{minipage}[b]{0.9\linewidth}
\small
\textbf{Foreword\,}
This chapter is an \emph{in extenso} reproduction of a manuscript under preparation for submission to Journal of Biomedical Optics. 
\newline
AB has conducted all of the research presented in this chapter under the supervision of JS, MB, and TV. 
\end{minipage}
\end{center}

@@

\section{Introduction}\label{sec:intro2}
The brain has many layered structures, for example the meninges (dura, pia mater, arachnoid) are all thin layer structures which overlay the cortex. As these are often of the scale that can be penetrated by visible light, this structure should be accounted for in an optical model used to analyse visible spectrum HSI data. Since Yudovsky 2009 was shown to be the best performing single layer model in Chapter~\ref{chap:1layer}, the double layer model of the same publication~\citep{Yudovsky2009} (developed primarily to model skin) is investigated.

@@

% Many methods have been used to quantify $StO_2$ in vivo \citep{Nitzan2020} with pulse oximetry being the most widely utilised non-invasive method, however these devices have been reported to have different performance quality with respect to different ethnicities \citep{Bangash2022}. More advanced, multi-layered, optical models of tissues have been proposed \citep{Maeda2010}. In this work we focus our analysis in the visible spectrum (450-650nm) as this allows for non-contact imaging using standard cold surgical light sources \citep{Clancy2011}. We investigate one multi-layered, analytical model proposed by Yudovsky et al. \citep{Yudovsky2009} which utilises a single layer model which we have previously shown demonstrates excellent results \citep{Bahl2023a}. The authors show the model to perform poorly above 600nm \citep{Yudovsky2011a} and so we restrict our evaluation range accordingly. 
% % from diffuse reflectance spectroscopy, however few model the spectrum per wavelength, and fewer still provide this modelled spectrum for skin which is characterised by a layered structure. A notable example of this is the Yudovsky 2009 \citep{Yudovsky2009} based on the Kubelka-Munk theory. 
% Whilst this model has been demonstrated with a variety of experimental data \citep{Yudovsky2011a, Yudovsky2011b},
% %there has not been a clear evaluation of its performance. 
% a systematic and reproducible evaluation of its performance is still lacking.

% % Yudovsky's two-layer model builds on a single-layer model which could also be used to capture average tissue parameters across layers.
% % In this work, we evaluate the two-layer model against the one-layer version
% % %we have also evaluated alongside
% % and also consider
% % two other prominent single-layer tissue models (a modified Beer-Lambert model \citep{Clancy2015}, and a more elaborate Beer-Lambert-based model proposed by Jacques \citep{Jacques1999}).
% % %\citep{Bahl2023a}.
% % These one-layer models are conceptually better suited to open surgical cases where the tissue seen can be approximated as a single homogeneous layer
% % and we refer the reader to our previous work for a head-to-head comparison in the single layer scenario \citep{Bahl2023a}.

@@

We also fit the two-layer model to experimental data made available by NIST~\citep{Cooksey2017}, and compare the extracted parameters to literature values. This allows us to evaluate the use of this model to solve the inverse problem.
This leads to a thorough evaluation of the Yudovsky two-layer model and enables informed application to clinical settings.

@@

In this work we specify the major components to be blood, melanin, and a background component accounting for all other chromophores whose impact are low in this wavelength range. This is shown in Equation~\eqref{eq:generalmua} where blood, melanin, and background are denoted $blood$, $mel$, and $back$ respectively.

@@

$c_{HbT}$ refers to the total concentration of haemoglobin in whole blood commonly taken as 150 gL$^{-1}$~\citep{Prahl1999}.

@@

The tissue parameters are restricted by Yudovsky to 20-100\% for $StO_2$, 0.2-7\% for $f_{blood}$~\citep{Yudovsky2011a} and we limit the scattering tissue parameters to 30-70cm$^{-1}$ and 0.7-2.5 for $a$ and $b$ respectively to reflect those of skin~\citep{Jacques2013}.

\subsubsection{Layered model formulation for diffuse reflectance}\label{sec:Yudovsky2009}
% The original Yudovsky model presents a complex analytical derivation \citep{Yudovsky2009} of a single-layer reflectance equation for each tissue layer with a simplified formulation subsequently presented in their Erratum \citep{Yudovsky2015}. The model takes the reduced albedo $w'(\lambda)$, calculated from $\mu_a$ and $\mu_s'$, as input and returns the diffuse reflectance spectra $R(\lambda)$.
% This provides an easily applicable model with hyperparameters $M_{1-6}$ which are quoted for a refractive index $n$ of 1.44. We found that hyperparameters $M_{1-6}$ can be fitted to Monte Carlo spectra to allow for use with other refractive indices \citep{Bahl2023a}. The hyperparameters found by fitting to a Monte Carlo dataset with a refractive index of 1.44 are used throughout this work \citep{Bahl2023a}. This simplified formulation is used within this work:
% \begin{equation}
% \begin{aligned}
%     & w'(\lambda) = \frac{\mu_s'(\lambda)}{\mu_a(\lambda) + \mu_s'(\lambda)} \\
%     & R = M_1 + M_2\exp{\left[ M_3w'(\lambda)^{M_4}\right]} + \frac{M_5}{1.02 - M_6} \\
% \end{aligned}
% \label{eq:Yudovskysingle}
% \end{equation} 
% 
The Yudovsky two-layer model is a complex interaction between two instances of the Yudovsky single-layer model~\citep{Yudovsky2009}, detailed in Section~\ref{sec:Yudovskysingle}, applied to two layers~\citep{Yudovsky2009}. 
These two layers represent the epidermis ($1$) and dermis ($2$), where the former has thickness $L_1$ and the latter is semi-infinite. $L_1$ is input to the model in units of cm, however it is discussed throughout in \textmu m for ease of interpretation.
These single layer reflectances are then combined as in Equation~\eqref{eq:Pilondouble} using a reduced reflectance ($R^*$) which is calculated using $L_1$, $w_{tr, 1}$, and $w_{tr,2}$ as 
%in Equation~\eqref{eq:reducedR}. 
shown below:
\begin{equation}
\begin{aligned}
    & \xi = \sqrt{\frac{47}{52} + \frac{31}{49}w_{tr, 1} - \frac{49}{54}w_{tr, 1}^2 - \frac{17}{27}w_{tr, 1}^3} \\
    & Y_1 = \xi(\mu_{a,1} + \mu_s')L_1 \\
    & \frac{1}{\alpha} = 2.562 - \frac{4.263}{3.050 - w_{tr, 2}} \\
    & R^* = \frac{\tanh{Y_1}}{\frac{1}{\alpha} + (1 - \frac{1}{\alpha})\tanh{Y_1}} \\
\end{aligned}
\label{eq:reducedR}
\end{equation} 
%Equation~\eqref{eq:Pilondouble} returns the diffuse reflectance spectrum, however this can be converted to total reflectance by addition of a constant offset of 0.0325 for a refractive index of 1.44 (for tissues)\citep{Yudovsky2011a}.
\begin{equation}
    R = R^*(R_{s1} - R_{s2}) + R_{s2}
\label{eq:Pilondouble}
\end{equation}
Whilst Equation~\eqref{eq:Pilondouble} returns diffuse reflectance values, Yudovsky et al. present a conversion to total reflectance ($R_{tot}$) values by addition of a wavelength independent specular reflectance ($R_{sp}$) term equalling 0.0325 for a refractive index of 1.44 as seen in Equation~\eqref{eq:Pilontotal}~\citep{Yudovsky2011a}.
\begin{equation}
    R_{tot} = R^*(R_{s1} - R_{s2}) + R_{s2} +R_{sp}
\label{eq:Pilontotal}
\end{equation}

\subsection{Inverse problem fitting to recover tissue parameters}\label{sec:methodinverse}
This formulation for reflectance presented in Section~\ref{sec:Yudovsky2009} ($R$) can be used to solve the inverse problem, shown in Equation~\eqref{eq:inverseproblem}, by fitting to a reflectance spectrum ($R_{ref}$). 
\begin{equation}
    \argmin_{StO_2, f_{blood}, f_{mel}, L_1, a, b} \sum || R_{ref}(\lambda) - R(\lambda) ||^2
    \label{eq:inverseproblem}
\end{equation}
This is fitted using a least squares fitting approach (using SciPy v1.10.0  \newline \href{https://docs.scipy.org/doc/scipy/reference/generated/scipy.optimize.least_squares.html}{\texttt{scipy.optimize.least\_squares}} function) which allows extraction of physiological parameters. 
Yudovsky et al. note that this model is not suitable for wavelengths above 600 nm~\citep{Yudovsky2011a} and therefore only wavelengths below 600nm are considered for this analysis. Similarly, Yudovsky et al. present results using wavelengths above 450 nm so we utilise the same wavelength range. We have found that increasing the weighting in the region 525-585nm, ie. the region corresponding to the major haemoglobin peaks, improves the fit of this model in this region. The weighting function used can be seen in \figref{fig:weighting} and is used throughout this work, however we provide similar analyses of the data with a uniform wavelength weighting in the Appendices Section~\ref{ap:2layeruniform}. 
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{fitting_region}
    \caption{Relative weighting of wavelengths used for least squares fitting of the two-layer Yudovsky model. The wavelengths considered are limited to 450-600nm to replicate those recommended by Yudovsky et al. An increased weighting is placed on the wavelength range 525-585nm to improve the visual fitting of this region which contains the major haemoglobin peaks.}
    \label{fig:weighting}
\end{figure}
Bounds are also imposed on the least squares fitting routine to ensure the fitted parameters are feasible and within a biologically relevant range for skin~\citep{Yudovsky2009, Jacques2013} such that:
\begin{itemize}
    \item 30cm$^{-1}$ $<=$ $a$ $<=$ 70cm$^{-1}$
    \item 0.7 $<= b <=$ 2.5
    \item 20\% $<= StO_2 <=$ 100\%
    \item 0.2\% $<= f_{blood} <=$ 7\% 
    \item 1\% $<= f_{mel} <=$ 43\% 
    \item 20{\textmu}m $<= L_1 <=$ 150{\textmu}m
\end{itemize}
Often in clinical settings it is difficult to obtain precise quantitative data and so relative data is used instead~\citep{Bahl2023}. For the
purposes of this work, we define relative data to be mean normalised spectra using the mean of all wavelengths in the range 450-600nm which can be applied to both $R$ and the simulated or measured data. 
%
%Often in clinical settings it is difficult to obtain precise quantitative data and so relative data is used instead\citep{Bahl2023}. For the purposes of this work, we define relative data to be mean normalised spectra using the mean of all wavelengths below 600nm.

\subsection{Reference spectra}\label{sec:methodreference2}
%100
\subsubsection{Simulated dataset}
Similarly to Section~\ref{sec:methodreference}, one hundred
Monte Carlo simulations are generated by selecting random values for the variables $a$, $b$, $StO_2$, $f_{blood}$, $f_{mel}$, and $L_1$ within the bounds detailed in Section~\ref{sec:methodinverse}.
%which are bounded to 30-70 cm$^{-1}$, 0.7-2.5, 20-100\%, 0.2-7\%, 1-43\%, and 20-150 {\textmu}m respectively to represent the range seen in skin \citep{Jacques2013, Yudovsky2009}.
These are converted to $\mu_a$ and $\mu_s'$ values as in \secref{sec:opticproperties2}. Monte Carlo takes $\mu_a$ and $\mu_s$ as inputs for each layer so a random value of $g$ is chosen per spectrum between 0.7-0.9 to convert $\mu_s'$ to $\mu_s$ using Equation~\eqref{eq:reducedscattering}. The diffuse reflectance spectra are then generated using CUDAMCML~\citep{Alerstam2008}, a GPU accelerated adaptation of the MCML programme for MC simulations of layered media with semi-infinite widths~\citep{Wang1995, Prahl1989}, to propagate 10000 photons through a geometry of a slab of thickness $L_1$ of epidermis with optical properties $\mu_{a,1}$ and $\mu_s'$ and a 3cm slab of dermis with optical properties $\mu_{a, 2}$ and $\mu_s'$. This depth is chosen to approximate a semi-infinite depth; for many tissues, the impact of increasing the depth of tissue is negligible beyond depths of 1 cm~\citep{Zhang2014}. When fitting models to these spectra for parameter extraction, the same bounds are imposed on the fitting routine.

\subsubsection{Measured dataset}
An existing NIST reflectance dataset made available by Cooksey et al.~\citep{Cooksey2017} is chosen to evaluate the model's performance on in vivo skin measurements. This dataset measured total reflectance from the forearms of 100 healthy volunteers using an integrating sphere spectrophotometer~\citep{Cooksey2017}. Three replicates were measured of which we utilise the mean for each volunteer to create the reference set of 100 spectra used for this work. This dataset is one of the few, or only, open access skin reflectance datasets and is chosen due to the high quality spectral measurement using a controlled integrating sphere measurement protocol. There are, however, no associated ground truth composition parameters for the subjects measured in this study. We also normalise this data by the mean of the wavelengths in the region 450-600nm to construct relative measured data for investigation. 
\FloatBarrier

@@

\subsubsection{Measured dataset}
The inverse problem can also be applied to the NIST skin dataset~\citep{Cooksey2017}. The model is fit to the total reflectance spectra in the NIST skin dataset. As there are no ground truth parameters available for this dataset, the recovered parameters from these 100 spectra are simply visualised as box and violin plots to compare to literature values for healthy individuals~\citep{Jacques2013, VanManen2021, Nishidate2011, Lintzeri2022}. \citet{VanManen2021} uses a modified Beer-Lambert-based model to analyse HSI images of skin using spatial regularisation, whereas \citet{Nishidate2011} uses a deep learning model trained using 3-layer Monte Carlo skin difuse reflectance simulations to analyse RGB images of skin. 
%\FloatBarrier

@@

\subsection{Simulated data}\label{sec:resultsMC2}
Spectra predicted by the forwards Yudovsky two-layer model are compared to those simulated by Monte Carlo simulated diffuse reflectance spectra. The mean ($\pm$ standard deviation) $NRMSE$ between the two for the same ground truth parameters at wavelengths in the range 450-600nm for a refractive index of 1.44 is 0.167($\pm$ 0.133) for quantitative data and 0.0402 ($\pm$ 0.0289) for relative data demonstrating considerable variability in the quality of fit for quantitative data which is significantly reduced by mean normalisation. This reduction in variability of fit can also be seen in some exemplar spectra shown in \figref{fig:egtwolayerMCforwards} and \figref{fig:egtwolayerMCforwardsnorm} for quantitative and relative data respectively. 
\begin{figure}[htbp]
    \centering
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{Compare_forwards_2_layer.pdf}
        \caption{Quantitative}
        \label{fig:egtwolayerMCforwards}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{Compare_forwards_2_layer_norm.pdf}
        \caption{Relative}
        \label{fig:egtwolayerMCforwardsnorm}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{StO2_twolayer_MC.pdf}
        \caption{Quantitative}
        \label{fig:egparamsStO2MC}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{StO2_twolayer_MC_norm.pdf}
        \caption{Relative}
        \label{fig:egparamsStO2MCnorm}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{2layer_parameter_exploration.pdf}
        \caption{Quantitative}
        \label{fig:egparamsfailureMC}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{2layer_parameter_exploration_norm.pdf}
        \caption{Relative}
        \label{fig:egparamsfailureMCnorm}
    \end{subfigure}
    \caption{Top: Demonstration of the variability of quality of fit between the Yudovsky 2009 two-layer model and Monte Carlo simulated diffuse spectra when using the same ground truth parameters for quantitative (left) or relative (right) data. Middle: Example $StO_2$ recovery from fitting Yudovsky 2009 two-layer model to Monte Carlo simulated diffuse reflectance and the associated linear regression line between the extracted and ground truth parameters for quantitative (left) or relative (right) data. Bottom: a depiction of the impact of 3 key physiological parameters on success of $StO_2$ extraction by visualising the Pearson $r$ correlation coefficient for the extracted $StO_2$ compared to the ground-truth for simulations with this range of parameters extracted using Yudovsky 2009 two-layer model for quantitative (left) or relative (right) data.}
    \label{fig:MC2layer}
\end{figure}

>>>>

\begin{center}
\begin{minipage}[b]{0.9\linewidth}
\small
\textbf{Foreword\,}
This chapter is an \emph{in extenso} reproduction of a manuscript under preparation for submission to Journal of Biomedical Optics. 
\newline
AB has conducted all of the research presented in this chapter under the supervision of JS, MB, and TV. \footnote{\annref{18}\textcolor{red}{AB:~Anisha Bahl, JS:~Jonathan Shapey, MB:~Mads Bergholt, TV:~Tom Vercauteren}}
\end{minipage}
\end{center}

@@

\section{Introduction}\label{sec:intro2}
The brain has many layered structures, for example the meninges (dura, pia mater, and arachnoid) are all thin layer structures which overlay the cortex. As these are often of the scale that can be penetrated by visible light, this structure should be accounted for in an optical model used to analyse visible spectrum HSI data. Since Yudovsky 2009 was shown to be the best performing single-layer model in Chapter~\ref{chap:1layer}, the double-layer model of the same publication~\citep{Yudovsky2009} (developed primarily to model skin) is investigated.

@@

% Many methods have been used to quantify $StO_2$ in vivo \citep{Nitzan2020} with pulse oximetry being the most widely utilised non-invasive method, however these devices have been reported to have different performance quality with respect to different ethnicities \citep{Bangash2022}. More advanced, multi-layered, optical models of tissues have been proposed \citep{Maeda2010}. In this work we focus our analysis in the visible spectrum (450-650nm) as this allows for non-contact imaging using standard cold surgical light sources \citep{Clancy2011}. We investigate one multi-layered, analytical model proposed by Yudovsky et al. \citep{Yudovsky2009} which utilises a single-layer model which we have previously shown demonstrates excellent results \citep{Bahl2023a}. The authors show the model to perform poorly above 600nm \citep{Yudovsky2011a} and so we restrict our evaluation range accordingly. 
% % from diffuse reflectance spectroscopy, however few model the spectrum per wavelength, and fewer still provide this modelled spectrum for skin which is characterised by a layered structure. A notable example of this is the Yudovsky 2009 \citep{Yudovsky2009} based on the Kubelka-Munk theory. 
% Whilst this model has been demonstrated with a variety of experimental data \citep{Yudovsky2011a, Yudovsky2011b},
% %there has not been a clear evaluation of its performance. 
% a systematic and reproducible evaluation of its performance is still lacking.

% % Yudovsky's two-layer model builds on a single-layer model which could also be used to capture average tissue parameters across layers.
% % In this work, we evaluate the two-layer model against the one-layer version
% % %we have also evaluated alongside
% % and also consider
% % two other prominent single-layer tissue models (a modified Beer-Lambert model \citep{Clancy2015}, and a more elaborate Beer-Lambert-based model proposed by Jacques \citep{Jacques1999}).
% % %\citep{Bahl2023a}.
% % These one-layer models are conceptually better suited to open surgical cases where the tissue seen can be approximated as a single homogeneous layer
% % and we refer the reader to our previous work for a head-to-head comparison in the single-layer scenario \citep{Bahl2023a}.

@@

We also fit the two-layer model to experimental data made available by the National Institute of Standards and Technology (NIST)~\citep{Cooksey2017}, and compare the extracted parameters to literature values. This allows us to evaluate the use of this model to solve the inverse problem.
This leads to a thorough evaluation of the Yudovsky two-layer model and enables informed application to clinical settings.

@@

In this work we specify the major components to be blood, melanin, and a background component accounting for all other chromophores \annref{48}\textcolor{red}{such as water or fat,} whose impact are low in this wavelength range. This is shown in Equation~\eqref{eq:generalmua} where blood, melanin, and background are denoted $blood$, $mel$, and $back$ respectively.

@@

$c_{HbT}$ refers to the total concentration of haemoglobin in whole blood commonly taken as 150~gL$^{-1}$~\citep{Prahl1999}.

@@

The tissue parameters are restricted by Yudovsky to 20-100\% for $StO_2$, 0.2-7\% for $f_{blood}$ \annref{49}\textcolor{red}{as is common for skin tissues and used by \citet{Yudovsky2011a}} and we limit the scattering tissue parameters to 30-70cm$^{-1}$ and 0.7-2.5 for $a$ and $b$ respectively to reflect those of skin~\citep{Jacques2013}.

\subsubsection{Layered model formulation for diffuse reflectance}\label{sec:Yudovsky2009}
% The original Yudovsky model presents a complex analytical derivation \citep{Yudovsky2009} of a single-layer reflectance equation for each tissue layer with a simplified formulation subsequently presented in their Erratum \citep{Yudovsky2015}. The model takes the reduced albedo $w'(\lambda)$, calculated from $\mu_a$ and $\mu_s'$, as input and returns the diffuse reflectance spectra $R(\lambda)$.
% This provides an easily applicable model with hyperparameters $M_{1-6}$ which are quoted for a refractive index $n$ of 1.44. We found that hyperparameters $M_{1-6}$ can be fitted to Monte Carlo spectra to allow for use with other refractive indices \citep{Bahl2023a}. The hyperparameters found by fitting to a Monte Carlo dataset with a refractive index of 1.44 are used throughout this work \citep{Bahl2023a}. This simplified formulation is used within this work:
% \begin{equation}
% \begin{aligned}
%     & w'(\lambda) = \frac{\mu_s'(\lambda)}{\mu_a(\lambda) + \mu_s'(\lambda)} \\
%     & R = M_1 + M_2\exp{\left[ M_3w'(\lambda)^{M_4}\right]} + \frac{M_5}{1.02 - M_6} \\
% \end{aligned}
% \label{eq:Yudovskysingle}
% \end{equation} 
% 
The Yudovsky two-layer model is a complex interaction between two instances of the Yudovsky single-layer model~\citep{Yudovsky2009}, detailed in Section~\ref{sec:Yudovskysingle}, applied to two layers~\citep{Yudovsky2009}. 
These two layers represent the epidermis ($1$) and dermis ($2$), where the former has thickness $L_1$ and the latter is semi-infinite. $L_1$ is input to the model in units of cm, however it is discussed throughout this work in \textmu m for ease of interpretation.
These single-layer reflectances are then combined as in Equation~\eqref{eq:Pilondouble} using a reduced reflectance ($R^*$) which is calculated using $L_1$, $w_{tr, 1}$, and $w_{tr,2}$ as 
%in Equation~\eqref{eq:reducedR}. 
shown below:
\begin{equation}
\begin{aligned}
    & \xi = \sqrt{\frac{47}{52} + \frac{31}{49}w_{tr, 1} - \frac{49}{54}w_{tr, 1}^2 - \frac{17}{27}w_{tr, 1}^3} \\
    & Y_1 = \xi(\mu_{a,1} + \mu_s')L_1 \\
    & \frac{1}{\alpha} = 2.562 - \frac{4.263}{3.050 - w_{tr, 2}} \\
    & R^* = \frac{\tanh{Y_1}}{\frac{1}{\alpha} + (1 - \frac{1}{\alpha})\tanh{Y_1}} \\
\end{aligned}
\label{eq:reducedR}
\end{equation} 
%Equation~\eqref{eq:Pilondouble} returns the diffuse reflectance spectrum, however this can be converted to total reflectance by addition of a constant offset of 0.0325 for a refractive index of 1.44 (for tissues)\citep{Yudovsky2011a}.
\begin{equation}
    R = R^*(R_{s1} - R_{s2}) + R_{s2}
\label{eq:Pilondouble}
\end{equation}
Whilst Equation~\eqref{eq:Pilondouble} returns diffuse reflectance values, Yudovsky et al. present a conversion to total reflectance ($R_{tot}$) values by addition of a wavelength independent specular reflectance ($R_{sp}$) term equalling 0.0325 (or 3.25\%) for a refractive index of 1.44 as seen in Equation~\eqref{eq:Pilontotal}~\citep{Yudovsky2011a}.
\begin{equation}
    R_{tot} = R^*(R_{s1} - R_{s2}) + R_{s2} +R_{sp}
\label{eq:Pilontotal}
\end{equation}

\subsection{Inverse problem fitting to recover tissue parameters}\label{sec:methodinverse}
This formulation for reflectance presented in Section~\ref{sec:Yudovsky2009} ($R_x$) can be used to solve the inverse problem, shown in Equation~\eqref{eq:inverseproblem}, by fitting to a reflectance spectrum ($R_{x,ref}$). 
\begin{equation}
    \argmin_{StO_2, f_{blood}, f_{mel}, L_1, a, b} \sum || R_{x,ref}(\lambda) - R_x(\lambda) ||^2
    \label{eq:inverseproblem}
\end{equation}
In Equation~\eqref{eq:inverseproblem} $x$ denotes the possibility for this to refer to diffuse or total reflectance spectra. This is fitted using a least squares fitting approach (using SciPy v1.10.0  \newline \href{https://docs.scipy.org/doc/scipy/reference/generated/scipy.optimize.least_squares.html}{\texttt{scipy.optimize.least\_squares}} function \selfref{7}\textcolor{red}{using the default settings alongside the bounds detailed for each parameter}) which allows extraction of physiological parameters. In this chapter, this fitting routine is used to fit the diffuse reflectance from Equation~\eqref{eq:Pilondouble} to simulated spectra, and the total reflectance from Equation~\eqref{eq:Pilontotal} to measured spectra.
Yudovsky et al. note that this model is not suitable for wavelengths above 600 nm~\citep{Yudovsky2011a} and therefore only wavelengths below 600nm are considered for this analysis. Similarly, Yudovsky et al. present results using wavelengths above 450 nm so we utilise the same wavelength range. We have found that increasing the weighting in the region 525-585nm, ie. the region corresponding to the major haemoglobin peaks, improves the fit of this model in this region. The weighting function used can be seen in \figref{fig:weighting} and is used throughout this work, however we provide similar analyses of the data with a uniform wavelength weighting in the Appendices Section~\ref{ap:2layeruniform}. 
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{fitting_region}
    \caption{Relative weighting of wavelengths used for least squares fitting of the two-layer Yudovsky model. The wavelengths considered are limited to 450-600nm to replicate those recommended by Yudovsky et al. An increased weighting is placed on the wavelength range 525-585nm to improve the visual fitting of this region which contains the major haemoglobin peaks.}
    \label{fig:weighting}
\end{figure}
Bounds are also imposed on the least squares fitting routine to ensure the fitted parameters are feasible and within a biologically relevant range for skin~\citep{Yudovsky2009, Jacques2013} such that:
\begin{itemize}
    \item $30cm^{-1} \leq a \leq 70cm^{-1}$
    \item $0.7 \leq b \leq 2.5$
    \item $20\% \leq StO_2 \leq 100\%$
    \item $0.2\% \leq f_{blood} \leq 7\% $
    \item $1\% \leq f_{mel} \leq 43\%$
    \item $20{\mu}m \leq L_1 \leq 150{\mu}m$
\end{itemize}
Often in clinical settings it is difficult to obtain precise quantitative data and so relative data is used instead~\citep{Bahl2023}. For the
purposes of this work, we define relative data to be mean normalised spectra using the mean of all wavelengths in the range 450-600nm. This can be applied to both simulated or measured reflectance spectra. 
%
%Often in clinical settings it is difficult to obtain precise quantitative data and so relative data is used instead\citep{Bahl2023}. For the purposes of this work, we define relative data to be mean normalised spectra using the mean of all wavelengths below 600nm.

\subsection{Reference spectra}\label{sec:methodreference2}
%100
\subsubsection{Simulated dataset}
Similarly to Section~\ref{sec:methodreference}, one hundred
Monte Carlo simulations are generated by selecting random values for the variables $a$, $b$, $StO_2$, $f_{blood}$, $f_{mel}$, and $L_1$ within the bounds detailed in Section~\ref{sec:methodinverse}.
%which are bounded to 30-70 cm$^{-1}$, 0.7-2.5, 20-100\%, 0.2-7\%, 1-43\%, and 20-150 {\textmu}m respectively to represent the range seen in skin \citep{Jacques2013, Yudovsky2009}.
These are converted to $\mu_a$ and $\mu_s'$ values as in \secref{sec:opticproperties2}. Monte Carlo takes $\mu_a$ and $\mu_s$ as inputs for each layer so a random value of $g$ is chosen per spectrum between 0.7-0.9 to convert $\mu_s'$ to $\mu_s$ using Equation~\eqref{eq:reducedscattering}. The diffuse reflectance spectra are then generated using CUDAMCML~\citep{Alerstam2008}, which is a GPU accelerated adaptation of the MCML programme~\citep{Prahl1989}. These produce MC simulations of layered media with semi-infinite widths~\citep{Wang1995, Prahl1989}. 10,000 photons are propagated through a geometry consisting of an epidermal slab of thickness $L_1$ with optical properties $\mu_{a,1}$ and $\mu_s'$ and a 3cm dermal slab with optical properties $\mu_{a, 2}$ and $\mu_s'$. The depth of 3cm is chosen to approximate a semi-infinite depth; for many tissues, the impact of increasing the depth of tissue is negligible beyond depths of 1 cm~\citep{Zhang2014}. %When fitting models to these spectra for parameter extraction, the same bounds are imposed on the fitting routine.

\subsubsection{Measured dataset}
An existing NIST reflectance dataset made available by \citet{Cooksey2017} is chosen to evaluate the model's performance on in vivo skin measurements. This dataset measured total reflectance from the forearms of 100 healthy volunteers using an integrating sphere spectrophotometer~\citep{Cooksey2017}. Three replicates were measured of which we utilise the mean for each volunteer to create the reference set of 100 spectra used for this work. This dataset is one of the few, or only, open access skin reflectance datasets and is chosen due to the high quality spectral measurement using a controlled integrating sphere measurement protocol. There are, however, no associated ground truth composition parameters for the subjects measured in this study. We also normalise this data by the mean of the wavelengths in the region 450-600nm to construct relative measured data for investigation. 
\FloatBarrier

@@

\subsubsection{Measured dataset}
The inverse problem can also be applied to the NIST skin dataset~\citep{Cooksey2017}. The model is fit to the total reflectance spectra in the NIST skin dataset. As there are no ground truth parameters available for this dataset, the recovered parameters from these 100 spectra are visualised as box and violin plots to compare to literature values for healthy individuals~\citep{Jacques2013, VanManen2021, Nishidate2011, Lintzeri2022}. \citet{VanManen2021} uses a modified Beer-Lambert-based model to analyse HSI images of skin using spatial regularisation, whereas \citet{Nishidate2011} uses a deep learning model trained using 3-layer Monte Carlo skin difuse reflectance simulations to analyse RGB images of skin. 
%\FloatBarrier

@@

\subsection{Simulated data}\label{sec:resultsMC2}
Diffuse reflectance spectra predicted by the forwards Yudovsky two-layer model are compared to Monte Carlo simulated diffuse reflectance spectra. The mean ($\pm$ standard deviation) $NRMSE$ between the two for the same ground truth parameters at wavelengths in the range 450-600nm for a refractive index of 1.44 is 0.167($\pm$ 0.133) for quantitative data and 0.0402 ($\pm$ 0.0289) for relative data demonstrating considerable variability in the quality of fit for quantitative data which is significantly reduced by mean normalisation. This reduction in variability of fit can also be seen in some exemplar spectra shown in \figref{fig:egtwolayerMCforwards} and \figref{fig:egtwolayerMCforwardsnorm} for quantitative and relative data respectively. 
\begin{figure}[htbp]
    \centering
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{Compare_forwards_2_layer.pdf}
        \caption{Quantitative}
        \label{fig:egtwolayerMCforwards}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{Compare_forwards_2_layer_norm.pdf}
        \caption{Relative}
        \label{fig:egtwolayerMCforwardsnorm}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{StO2_twolayer_MC.pdf}
        \caption{Quantitative}
        \label{fig:egparamsStO2MC}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{StO2_twolayer_MC_norm.pdf}
        \caption{Relative}
        \label{fig:egparamsStO2MCnorm}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{2layer_parameter_exploration.pdf}
        \caption{Quantitative}
        \label{fig:egparamsfailureMC}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{2layer_parameter_exploration_norm.pdf}
        \caption{Relative}
        \label{fig:egparamsfailureMCnorm}
    \end{subfigure}
    \caption{Top: Demonstration of the variability of quality of fit between the Yudovsky 2009 two-layer model and Monte Carlo simulated diffuse reflectance spectra when using the same ground truth parameters for quantitative (left) or relative (right) data. Middle: Example $StO_2$ recovery from fitting Yudovsky 2009 two-layer model to Monte Carlo simulated diffuse reflectance and the associated linear regression line between the extracted and ground truth parameters for quantitative (left) or relative (right) data. Bottom: a depiction of the impact of 3 key physiological parameters on success of $StO_2$ extraction by visualising the Pearson $r$ correlation coefficient for the extracted $StO_2$ compared to the ground-truth for simulations with this combination of parameters extracted using Yudovsky 2009 two-layer model for quantitative (left) or relative (right) data.}
    \label{fig:MC2layer}
\end{figure}

When fitting the model to the Monte Carlo dataset, the $a$, $b$, $StO_2$, $f_{blood}$, $f_{mel}$, and $L_1$ parameters are extracted and compared to the ground truth Monte Carlo inputs using a linear regression. The regression gradient $m$ and offset $c$ between these retrieved values and the ground truth counterparts, alongside the Pearson $r$ values (bold if $p<0.05$ which is considered significant), and the mean ($\pm$ standard deviation) absolute percentage errors (APE) are shown in \tabref{tb:doubleparamtrends}. An example of the fitted parameters compared to the ground truth parameters is shown for $StO_2$ in  \figref{fig:egparamsStO2MC} for quantitative data and  \figref{fig:egparamsStO2MCnorm} for relative data. This shows parameter extraction to be significantly poorer than for the single-layer model and parameter extraction from quantitative data performing similarly that of relative data for $StO_2$ but better for all others. 
\begin{table}[t]
    \caption{The regression gradient $m$, offset $c$, Pearson $r$ (bold if $p<0.05$), and the mean ($\pm$ standard deviation) absolute percentage errors (APE) for each variable when extracted by fitting Yudovsky 2009 two-layer model to the quantitative or relative Monte-Carlo diffuse reflectance dataset. All presented to 3s.f.}
    \begin{tabular}{|c|c|cccc|}
        Parameter & Quantitative & $m$ & $c$ & $r$ & Mean ($\pm$ Standard  \\
        & or Relative & (ideal =1) & (ideal = 0) & (ideal = 1) & deviation) APE (\%)\\
        \multirow{2}{*}{$StO_2$} & Quantitative & 0.844 & 10.2 & \textbf{0.788} & 15.3($\pm$ 27.5) \\
        & Relative & 0.827 & 8.99 & \textbf{0.836} & 13.1($\pm$ 19.7) \\
        \multirow{2}{*}{$f_{blood}$} & Quantitative & 0.948 & 0.270 & \textbf{0.852} & 24.0($\pm$ 23.9) \\
        & Relative & 0.784 & 0.216 & \textbf{0.672} & 32.4($\pm$ 27.8) \\
